lfl: An \R{} Package for Linguistic Fuzzy Logic

### 2021-06-09 chunks/chunk-casestudy-assoc-lcut.tex
...

\begin{Schunk}
% --begin: "casestudy-assoc-lcut"
\begin{Sinput}
ldata <- lcut(data)
colnames(ldata)
\end{Sinput}
\begin{Soutput}
##  [1] "position=accountant" "position=manager"    "position=worker"    
##  [4] "ex.sm.age"           "si.sm.age"           "ve.sm.age"          
##  [7] "sm.age"              "ml.sm.age"           "ro.sm.age"          
## [10] "qr.sm.age"           "vr.sm.age"           "ty.me.age"          
## [13] "me.age"              "ml.me.age"           "ro.me.age"          
## [16] "qr.me.age"           "vr.me.age"           "ex.bi.age"          
## [19] "si.bi.age"           "ve.bi.age"           "bi.age"             
## [22] "ml.bi.age"           "ro.bi.age"           "qr.bi.age"          
## [25] "vr.bi.age"           "employed"            "not.employed"       
## [28] "ex.sm.salary"        "si.sm.salary"        "ve.sm.salary"       
## [31] "sm.salary"           "ml.sm.salary"        "ro.sm.salary"       
## [34] "qr.sm.salary"        "vr.sm.salary"        "ty.me.salary"       
## [37] "me.salary"           "ml.me.salary"        "ro.me.salary"       
## [40] "qr.me.salary"        "vr.me.salary"        "ex.bi.salary"       
## [43] "si.bi.salary"        "ve.bi.salary"        "bi.salary"          
## [46] "ml.bi.salary"        "ro.bi.salary"        "qr.bi.salary"       
## [49] "vr.bi.salary"
\end{Soutput}
%
% --end: "casestudy-assoc-lcut"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "casestudy-assoc-lcut"
\begin{Sinput}
ldata <- lcut(iris)
\end{Sinput}
%
% --end: "casestudy-assoc-lcut"
\end{Schunk}

### 2021-06-09 chunks/chunk-casestudy-assoc-reduce.tex
...

\begin{Schunk}
% --begin: "casestudy-assoc-reduce"
\begin{Sinput}
reduce(ldata, rules=lrules, ratio=1)
\end{Sinput}
\begin{Soutput}
## Empty rule base
\end{Soutput}
%
% --end: "casestudy-assoc-reduce"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "casestudy-assoc-reduce"
\begin{Sinput}
r <- reduce(ldata, rules=lrules, ratio=1)
rownames(as.data.frame(r))
\end{Sinput}
\begin{Soutput}
##  [1] "qr.sm.Petal.Width => Species=setosa"                                              
##  [2] "ro.me.Sepal.Width & qr.sm.Petal.Length => Species=setosa"                         
##  [3] "ve.sm.Sepal.Length => Species=setosa"                                             
##  [4] "ro.me.Sepal.Length & ml.me.Petal.Length & ty.me.Petal.Width => Species=versicolor"
##  [5] "ty.me.Petal.Length => Species=versicolor"                                         
##  [6] "ro.bi.Petal.Length => Species=virginica"                                          
##  [7] "ml.bi.Petal.Width => Species=virginica"                                           
##  [8] "vr.sm.Sepal.Width & ro.bi.Petal.Width => Species=virginica"                       
##  [9] "qr.bi.Petal.Length & ro.bi.Petal.Width => Species=virginica"                      
## [10] "vr.bi.Sepal.Length & ro.bi.Petal.Width => Species=virginica"
\end{Soutput}
%
% --end: "casestudy-assoc-reduce"
\end{Schunk}
